Test susieI using chr17 to 22

### 2020-09-04 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
susieI more runs

# susieI genes - setting 1

@@

# susieI genes - setting 2

@@

# susieI genes - setting 3

@@

# susieI genes - setting 4

@@

# susieI genes - setting 5

@@

# susieI genes - setting 6

>>>>

# susieI (filtered regions) - setting 1

@@

# susieI (filtered regions) - setting 2

* Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3.

* Susie run parameters: `L=2`, initialize `null_weight = 0`, update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform.

Prior change for each iteration:
```{r iter-6}
load(paste0(outputdir, tag, ".config6.susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

```{r param-6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config6.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config6.susieI.txt")

# susieI (filtered regions) - setting 3

* Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3.

* Susie run parameters: `L=2`, initialize `null_weight = 0`, update `null_weight` in iterations. We initialize with prior for genes and SNPs as 0.05 and 2.5e-3.

Prior change for each iteration:
```{r iter-8}
load(paste0(outputdir, tag, ".config8.susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

```{r param-8}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config8.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config8.susieI.txt")

# susieI (filtered regions) - setting 4

* Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3.

* Susie run parameters: `L=2`, `null_weight = 0`. Didn't update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform.

Prior change for each iteration:
```{r iter-7}
load(paste0(outputdir, tag, ".config7.susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

```{r param-7}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config7.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config7.susieI.txt")

# susieI (all regions) - setting 1

@@

# susieI (all regions) - setting 2

@@

# susieI (all regions) - setting 3

@@

# susieI (all regions) - setting 4

@@

# susieI (all regions) - setting 5
